---
title: "WP4_phy_Baltic_fix.Rmd"
author: "Luuk van der Heijden, modified by Markus Lindh"
date: "15 june 2020, modified 2020-09-28"
output: html_document
---

# There are a couple of files that are needed in this script that we have not generated in previous scripts. Overall there are many fixes in this script that we skip for now.

# Global options

```{r global_options}
knitr::opts_chunk$set(echo = TRUE)
require(robis)
require(lubridate)
require(tidyverse)
```

# Here we load the data that has been extracted from the OBIS server. 

In the next step of the analysis, we make a list of data sets, check for the largest which with we start. Then we look up their metadata and store this information in a .csv file. We determine their number of unique phytoplankton species.

In a manual selection step, we fill a field called 'include' to determine what datasets we are going to use in subsequent analysis. We re-read the .csv file and use it to collect the final set of records to be used. We store these records in a binary file.


```{r manipulating of datasets}
# Load these records with data
all2Data <- read_delim(file.path("data/derived_data/all2Data.csv"), delim = ";")
```

# Here we do some manual repairs on datasets that are still not usable. 

```{r fix a number of datasets}
fix_phy <- all2Data %>%
  distinct(aphiaidaccepted, datasetid, datecollected, decimallatitude, decimallongitude, .keep_all = TRUE) %>%       # Select distinct objects
  filter(!datecollected %in% NA) %>%                                                                                 # Remove obs. without date (9)
  mutate(date = as.Date.POSIXct(datecollected)) %>%                                                                  # Make sure all dates are in one format
  mutate(month = lubridate::month(datecollected)) %>%                                                                # Create column with months
  mutate(year = lubridate::year(datecollected)) %>%                                                                  # Create column with years
  mutate(datasetID = as.numeric(datasetID)) %>%                                                                      # Make numeric
  unite(eventID_2, c("datecollected", "decimallatitude", "decimallongitude"), sep = "-", remove = FALSE) %>%         # Make eventID were not present
  mutate(eventIDnew = ifelse(is.na(eventid), eventID_2, eventid)) %>%
  mutate(aphiaid_new = str_extract(aphiaidaccepted, "[^http://marinespecies.org/aphia.php?p=taxdetails&id=]+$")) %>% # Remove website from aphiaid
  select(-eventid, -eventID_2, -coordinateuncertaintyinmeters, -aphiaidaccepted, -aphiaid) %>%                       # Remove columns not necessary
  rename(eventid = eventIDnew, aphiaid = aphiaid_new)                                                             # Rename these columns created

# Save file
save(fix_phy, file = "data/derived_data/fix_phy.Rdata")
```

# Reproducibility

```{r reproducibility}
# Date time
Sys.time()

# Here we store the session info for this script
sessioninfo::session_info()
```